How do school travel planning stakeholders frame active school travel in Ontario, Canada?

### 2021-07-09 AST-Framing-Ontario/AST-Framing-Ontario.Rmd
Update kwic code with raw policy corpus
If using the cleaned policy corpus, the context around the keyword (as identified using the kwic function from quanteda) is somewhat distorted as stop words and punctuation have been removed. Using the raw policy corpus (not cleaned) yields more useful information.

```{r policy-concordance, echo=FALSE}
# Import VCorpus created by tm package

policy_quanteda <- tm::VCorpus(tm::VectorSource(policy_corpus))
policy_quanteda <- corpus(policy_quanteda)

@@

kwic_pol_physical <- kwic(tokens(policy_quanteda), pattern = "physical")
kwic_pol_mental <- kwic(tokens(policy_quanteda), pattern = "mental")
kwic_pol_air <- kwic(tokens(policy_quanteda), pattern = "air")
kwic_pol_traffic <- kwic(tokens(policy_quanteda), pattern = "traffic")
kwic_pol_safety <- kwic(tokens(policy_quanteda), pattern = "safety")
kwic_pol_health <- kwic(tokens(policy_quanteda), pattern = "health")
kwic_pol_emissions <- kwic(tokens(policy_quanteda), pattern = "emissions")
kwic_pol_routes <- kwic(tokens(policy_quanteda), pattern = "routes")
kwic_pol_lanes <- kwic(tokens(policy_quanteda), pattern = "lanes")
kwic_pol_zone <- kwic(tokens(policy_quanteda), pattern = "zone")
kwic_pol_bus <- kwic(tokens(policy_quanteda), pattern = "bus")
kwic_pol_comm <- kwic(tokens(policy_quanteda), pattern = "community")
kwic_pol_ben <- kwic(tokens(policy_quanteda), pattern = "benefit")
kwic_pol_wea <- kwic(tokens(policy_quanteda), pattern = "weather")
kwic_pol_lanes <- kwic(tokens(policy_quanteda), pattern = "lanes")
```

>>>>

```{r policy-concordance, echo=FALSE}
# Import raw policy VCorpus (not cleaned of stop words or punctuation) created by tm package

policy_quanteda <- tm::VCorpus(tm::VectorSource(raw_policy_corpus))
policy_quanteda <- corpus(policy_quanteda)

@@

kwic_pol_physical <- kwic(tokens(policy_quanteda), pattern = "physical", window = 10)
kwic_pol_mental <- kwic(tokens(policy_quanteda), pattern = "mental", window = 10)
kwic_pol_air <- kwic(tokens(policy_quanteda), pattern = "air", window = 10)
kwic_pol_traffic <- kwic(tokens(policy_quanteda), pattern = "traffic", window = 10)
kwic_pol_safety <- kwic(tokens(policy_quanteda), pattern = "safety", window = 10)
kwic_pol_health <- kwic(tokens(policy_quanteda), pattern = "health", window = 10)
kwic_pol_emissions <- kwic(tokens(policy_quanteda), pattern = "emissions", window = 10)
kwic_pol_routes <- kwic(tokens(policy_quanteda), pattern = "routes", window = 10)
kwic_pol_lanes <- kwic(tokens(policy_quanteda), pattern = "lanes", window = 10)
kwic_pol_zone <- kwic(tokens(policy_quanteda), pattern = "zone", window = 10)
kwic_pol_bus <- kwic(tokens(policy_quanteda), pattern = "bus", window = 10)
kwic_pol_comm <- kwic(tokens(policy_quanteda), pattern = "community", window = 10)
kwic_pol_ben <- kwic(tokens(policy_quanteda), pattern = "benefit", window = 10)
kwic_pol_wea <- kwic(tokens(policy_quanteda), pattern = "weather", window = 10)
kwic_pol_lanes <- kwic(tokens(policy_quanteda), pattern = "lanes", window = 10)
```
